Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
make editorial change

Here we describe the scheme between the classical client and an honest quantum server. We mostly follow the logic in \cite{1804.01082}. We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.
Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.

We pick our universal gate set to be Hadamard gate and controlled phase gate:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
We know this is universal from (TODO cite Kitaev). So each $U_i\in\set{H, \Lambda(P(i))}$

@@

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re|\psi\rangle+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$

@@

We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.

>>>>

Here we describe the scheme between the classical client and an honest quantum server. We mostly follow the logic in \cite{1804.01082}. We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.

We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$

@@

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re|\psi\rangle+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
We then double (TODO: maybe multiply by $\gamma>1$ instead of doubling?) the size of the circuit by padding identity matrices at the end.
After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.

@@
